Suppl. Figure 1. Bacterial abundance across datasets

### 2022-01-31 reports/rmarkdown/manuscript/Suppl.Figure1.Rmd
minor changes

---
title: "Bacterial abundance across datasets"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(niceRplots)
})  })  })

@@

```{r Bacterial abundance, echo = FALSE, eval = TRUE, fig.height=3, fig.width=7}
par(mar=c(6,2.5,1,1)) #b,l,t,r

@@

x <- t(sapply(datasets_all_samples[2:3],function(x){
  c(t(x))
}))
colnames(x) <- c(sapply(rownames(datasets_all_samples[[2]]),
                        function(i){rep(i,ncol(datasets_all_samples[[2]]))}))
#rownames(x) <- gsub("ASV_|_norm.*", "",rownames(x))
rownames(x) <- c("Tissue", "Luminal")

>>>>

---
title: "Suppl. Figure 1. Bacterial abundance across datasets"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

```{r Bacterial abundance, echo = FALSE, eval = TRUE,  fig.asp=.5}
par(mar=c(6,2.5,0,0)) #b,l,t,r

@@

x <- t(sapply(datasets_all_samples[2:3],function(x){
  c(t(x))
}))
colnames(x) <- c(sapply(rownames(datasets_all_samples[[2]]),
                        function(i){rep(i,ncol(datasets_all_samples[[2]]))}))

rownames(x) <- c("Tissue", "Luminal")
